%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

    %---------------------------------------------------------
    \cventry
    {canuslector.site} % Institution
    {Personal | Full Stack} % Degree
    {Buenos Aires, Argentina} % Location
    {Sep. 2018 - Aug. 2018} % Date(s)
    {
    \begin{cvitems} % Description(s) bullet points
        \item {Personal site where I post most of my readings, for this project I used Vuejs, Node, Mysql for development and AWS EC2/S3 as Infra.}
    \end{cvitems}
    }
    %---------------------------------------------------------

    \cventry
    {Blog post of this project: lucascontre.site} % Institution
    {Edrans | Full Stack Dev. + Microservices} % Degree
    {Las Vegas, USA} % Location
    {Jan. 2019 - May. 2019} % Date(s)
    {
    \begin{cvitems} % Description(s) bullet points
        \item {Co-developed in the development of an application that interconnects and interacts with several Microservices using Python, Flask, Serverless, Node and Vuejs}
    \end{cvitems}
    }
    %---------------------------------------------------------
    \cventry
    {AntiplagaNorte Management system} % Institution
    {Codelamp | Full Stack Dev.} % Degree
    {Buenos Aires, Argentina} % Location
    {Jan. 2019 - May. 2019} % Date(s)
    {
    \begin{cvitems} % Description(s) bullet points
        \item {Co-developed an application that merges all of the activities performed in AntiplagaNorte into a single app, generating useful data and dealing with a complicated domain logic. For this project we used PHP, Laravel and MySQL and interacted with the OpenWeather APIs}
    \end{cvitems}
    }
    %---------------------------------------------------------
    \cventry
    {} % Degree
    {} % Institution
    {} % Location
    {} % Date(s)
    {
    \begin{cvitems} % Description(s) bullet points
        \item {For further projects and success cases, please refer to lucascontre.site}
    \end{cvitems}
    }

\end{cventries}

