%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
{Site Reliability Engineer} % Job title
{Edrans} % Organization
{Argentina - USA} % Location
{Jun. 2018 - Present} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {Co-developed a full Serverless app with 3 fully composable Microservices/APIs using Python and NodeJS in AWS}
\item {Solve several IaC issues with both Serverless, and CloudFormation in AWS and automate a handful of procedures using Docker and Docker-compose}
\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Freelance Developer} % Job title
{Codelamp} % Organization
{Argentina} % Location
{Sep. 2013, Present} % Date(s)
{
\begin{cvitems}
    \item {I have to dealt with most aspects of development, from writing a functional brief to designing, coding, selling and maintaining the software.}
\end{cvitems}
}

%---------------------------------------------------------
\cventry
{Full Stack Developer} % Job title
{Go Soluciones y Sistemas} % Organization
{Argentina - Uruguay} % Location
{May. 2018 - Jun. 2018} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {Developed several modules of a system that tracks trucks and sends a report over GPS signal in order to calculate trips' costs depending on different variables and had to interact with the SAP API in order generate ready-to-print invoices from within the system I was developing.}
\end{cvitems}
}

%---------------------------------------------------------
\cventry
{System Security Intern} % Job title
{Toyota S.A} % Organization
{Argentina} % Location
{Dec. 2016 - Dec. 2017} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {Administrated Active Directory, MySQL and Windows Servers as well as Massive software installation procedures with InvGate software}
\end{cvitems}
}
%---------------------------------------------------------
\end{cventries}
