%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
\cventry
{Site Reliability Engineer} % Job title
{Edrans} % Organization
{Argentina - USA} % Location
{Jun. 2018 - Present} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {Co-developed a full Serverless app with 3 fully composable Microservices/APIs using Python and NodeJS}
\item {Solve several IaC issues with both Serverless, and CloudFormation in AWS}
\item {Automate a handful of procedures using Docker and Docker-compose}
\item{Interact with software like Sensu, Nagios, Jira, Influx, Telegraf and Grafana}
\end{cvitems}
}


%---------------------------------------------------------
\cventry
{Fullstack Developer} % Job title
{Go Soluciones y Sistemas} % Organization
{Argentina - Uruguay} % Location
{May. 2018 - Jun. 2018} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {Developed several modules of a system that tracks trucks and sends a report over GPS signal in order to calculate trips' costs depending on different variables.}
\item {During my short work on Go Soluciones I also had to interact with the SAP API in order generate ready-to-print invoices from within the system I was developing.}
\end{cvitems}
}


%---------------------------------------------------------
\cventry
{System Security Intern} % Job title
{Toyota S.A} % Organization
{Argentina} % Location
{Dec. 2016 - Dec. 2017} % Date(s)
{
\begin{cvitems} % Description(s) of tasks/responsibilities
\item {Had to deal with Active Directory and MySQL user's permissions and creation, Windows Server administration, and Massive software installation procedures.}
\item {Studied and understood the importance of processes in large-scale companies and how they lead directly to concrete and measurable results.}
\item {I incorporated the TPS principles into my day-to-day life which led to significant improvements in my work.}
\end{cvitems}
}


%---------------------------------------------------------
\cventry
{Freelance Developer} % Job title
{Codelamp} % Organization
{Argentina} % Location
{Sep. 2013, Present} % Date(s)
{
\begin{cvitems}
As a freelance developer, together with my partner we had to deal most aspects of development. From writing a functional brief to designing and coding the entire software, selling and maintaining it.
Dealing with the arbitrary complexity different clients can add to the process of coding led us to try new development methodologies and learn new technologies.
\end{cvitems}
}


%---------------------------------------------------------
\end{cventries}
